---
title: "Using the larinf package"
author: "Karl Gregory"
date: "`r Sys.Date()`"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Install with the R commands:

```{r echo = FALSE}
library(larinf)
```


```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("gregorkb/larinf")
```

See the package documentation for details. 

# Illustration on example data set

Compute and plot the least angle regression path for the response vector and design matrix in the data set `facetemp`, which is included in the `larinf` package:

```{r lar}
data(facetemp)
X <- facetemp$X
y <- facetemp$y

lar_out <- lar(X,y)
plot(lar_out)
```


Obtain bootstrap confidence intervals for the entrance correlations and make a plot comparing inference on the least angle regression entrance correlations to classical inference on the regression coefficients:
```{r larinf}
larinf_out <- larinf(X,y)
plot(larinf_out,omaadd=c(0,0,1,1))
```


Print the estimated entrance correlations with 95\% confidence intervals:
```{r larinf_print}
larinf_out
```
